---
title: "Bridge2AI self-identified expertise analysis"
author: "Sean Davis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bridge2AI self-identified expertise analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Setup

```{r message=FALSE}
library(dplyr)
library(tidyr)
library(ComplexHeatmap)
library(readr)
library(DT)
library(B2AITeamingScratchpad)
library(heatmaply)
library(ggplot2)
```

## Load data

Just to keep things simple, I exported the `dsSrc` tab as a csv file from [this spreadsheet](https://docs.google.com/spreadsheets/d/1hSSzTlXJUrSMNfzvISZDAsmViOU5dWfU48a7xU9_iss/edit?usp=sharing) (owned by Julie).

```{r message=FALSE}
dssrc = dssrc_dataframe()
dplyr::glimpse(dssrc)
```

# Distributions

```{r}
person_expertise = dssrc |> 
  dplyr::select(fullName, `expertise-all`) |> 
  dplyr::arrange(fullName, `expertise-all`) |> 
  dplyr::mutate(`expertise-all`=tolower(`expertise-all`)) |> 
  dplyr::mutate(`expertise-all` = gsub('\\(.*\\)', '', `expertise-all`)) |>
  tidyr::separate_longer_delim(`expertise-all`, ', ') |> 
  unique()

head(person_expertise)
```

## Histogram of expertise count by person

```{r}
expertise_count_by_person = person_expertise |> 
  dplyr::group_by(fullName) |>
  dplyr::summarise(count=dplyr::n())
ggplot(expertise_count_by_person, aes(x=count)) + 
  geom_histogram() +
  ggplot2::ggtitle("Expertise Count By Person", "All onboarded individuals") +
  ggplot2::ylab('People')
```

```{r}
people_count_by_expertise = person_expertise |>
  dplyr::group_by(`expertise-all`) |>
  dplyr::summarise(count=dplyr::n()) |> 
  dplyr::arrange(dplyr::desc(count))
ggplot(people_count_by_expertise, aes(x=count)) +
  ggplot2::geom_histogram() +
  ggplot2::ggtitle("Person Count per Expertise", "All onboarded individuals") +
  ggplot2::ylab('Expertise')
```

## Top Expertise

```{r}
DT::datatable(people_count_by_expertise)
```

## Two-dimensional clustering

```{r}
person_by_expertise = person_expertise |> 
  dplyr::mutate(value=1) |> 
  tidyr::pivot_wider(names_from=fullName, values_from = value)

# Now a matrix of 0/1 (integer)
person_by_expertise_01 = as.matrix(person_by_expertise[,-1])
colnames(person_by_expertise_01) = colnames(person_by_expertise[,-1])
rownames(person_by_expertise_01) = person_by_expertise$`expertise-all`
person_by_expertise_01[is.na(person_by_expertise_01)] = 0
```

And now the two-dimensional (heatmap) plot that is interactive.

-   Draw a box to zoom as needed.

-   Double-click to return to full dataset:

```{r}
library(heatmaply)
heatmaply::heatmaply(person_by_expertise_01,col = c('lightblue','black'), hide_colorbar=TRUE, fontsize_row=4, fontsize_col=4, plot_method='ggplot')
```

To make a large PDF version of the figure, use the following code:

```{r}
pdf('expertise_matrix.pdf',height=30,width=50)
ComplexHeatmap::Heatmap(
  person_by_expertise_01, 
  column_names_gp = grid::gpar(fontsize=12), 
  row_names_gp = grid::gpar(fontsize=12), 
  col=c('gray95', 'black'), 
  row_dend_width = unit(30, "mm"), 
  column_dend_height = unit(30, 'mm'))
dev.off()
```

